### 2020-09-30 paper_29_09_2020/paper_29_09_2020.tex
versao do dia 29-09-2020

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}

\usepackage{color}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}

@@

\begin{abstract}\noindent
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better alternative than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

@@

The mechanism by adding shape parameters to a baseline distribution has
proved to be useful to make the generated distributions more flexible especially for studying tail
properties than existing distributions and for improving their goodness-of-fit statistics
to the data under study.

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
parameter vectot $\eta$. A generalized family are presented
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

@@

The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
each one having a gamma density unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defined the PDF of the minimum $W_1,\cdots,W_n$. 
Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
on applications.

Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
more flexibility for these functions in relation to the baseline ones.

@@

\begin{figure}[H]
\begin{center}
(a)\hspace{3.5cm} (b)\\
\includegraphics[scale=.3]{density.pdf}
\includegraphics[scale=.3]{hazard.pdf}\\
\vspace{-0.5cm}
\caption{(a) Curves for the MO-$\Gamma$-W density. (b) Curves for the MO-$\Gamma$-W hazard.\label{formas}}
\end{center}
\end{figure}

@@

The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to determine the quantile function (QF) of the MO-$\Gamma$-G distribution,
say $x=Q_{X}(u)$, in terms of the baseline QF $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, it follows $z=z(u)=\theta u/[1-(1-\theta)u]$.
Then, the QF of $X$ takes the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is an upper point
corresponding to the quantile $z$ of a gamma density (with unit scale and shape $\alpha$).

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
\end{table}
\end{landscape}

@@

To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020). This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN. With it, in particular using the function {\tt goodness.fit} it is possible to pass an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of the function {\tt goodness.fit} obtain $\ell (\cdot)$ by returning several measures of fit adequacy as well as MLEs. Further details regarding the {\bf AdequacyModel} package can be obtained from Marinho et al. (2019).

@@

\begin{table}[H]
	\centering
	\caption{Average biases of the MLEs obtained using the BFGS method.}\label{tab:bias}
	\begin{tabular}{rrrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
		\hline
		10 & 0.2376 & 2.1635 & 2.7557 & 1.6282 & 1.3057 & 1.1430\\
		20 & 0.4154 & 2.4639 & 1.5728 & 1.8082 & 0.7383 & 1.6248\\
		60 & 0.7214 & 2.2432 & 0.5667 & 1.8815 & 0.2872 & 3.3954\\
		100 & 0.6146 & 1.9579 & 0.3253 & 1.6148 & 0.2651 & 4.9628\\
		200 & 0.3838 & 1.3894 & 0.1827 & 1.1773 & 0.3701 & 8.1457\\
		400 & 0.2166 & 0.9635 & 0.1076 & 0.6181 & 0.3957 & 13.7370\\
		600 & 0.1269 & 0.7242 & 0.0772 & 0.3968 & 0.3637 & 17.9310\\
		1,000 & 0.0553 & 0.4885 & 0.0521 & 0.2328 & 0.2636 & 22.8784 \\
		2,000  &  0.0456 & 0.3087 &  0.0334 &  0.0990 & 0.1722 &  38.4593\\
		5,000 & -0.0058 & 0.1307 & 0.0146 & 0.0117 & 0.0171 & 52.8098\\
		10,000 & -0.0146 & 0.0842 & 0.0095 & 0.0095 & 0.0031 & 95.8380\\
		20,000 & -0.0090 & 0.0330 & 0.0038 & 0.0005 & -0.0099 & 126.4260\\
		30,000 & -0.0028 & 0.0183 & 0.0012 & -0.0036 & -0.0029 & 182.0760\\
		50,000 & -0.0057 & 0.0124 & 0.0015 & 0.0016 & -0.0021 & 291.9300\\
		\hline
	\end{tabular}
\end{table}

@@

>>>>

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}
\usepackage{xcolor}
\usepackage{color}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}

@@

\begin{abstract}\noindent
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

@@

The mechanism by adding shape parameters to a baseline distribution has
proved to be useful to make the generated distributions more flexible especially for studying tail
properties than existing distributions and for improving their goodness-of-fit statistics
to the data under study. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
parameter vectot $\eta$. A generalized family are presented
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas.

@@

The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
each one having a gamma density unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defines the PDF of the minimum $W_1,\cdots,W_n$. 
Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
on applications.

Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
more flexibility for these functions in relation to the baseline ones.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale =  0.39]{pdf-hazard.pdf}
\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
\end{center}
\end{figure}

@@

The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
Then, the QF of $X$ can be expressed as
$$x=Q_G\left(v(u)\right),$$
where
$$v(u)=1-\exp\left[-\gamma_1^{-1}\big(a,z(u)\big)\right],$$
and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
$Q^{-1}(a,1-w)$ are given in \url{http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/}.

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
\end{table}
\end{landscape}

@@

To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020). This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.  With it, in particular using the goodness.fit function, it is possible to provide an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of this function, obtain $\ell(\cdot)$  by returning several measures of fit adequacy as well as the MLEs. Further details regarding this package can be obtained from Marinho et al. (2019).

@@

{\color{red}

Para gerar obervações da variável aleatória $X$ com distribuição $G$ optou-se em considerar  o algoritmo do método da aceitação e rejeição, muito útil quando a função quantilica envolvem funções complexas que podem trazer algumas imprecisões numéricas.  Seja $X$ uma variável aleatória com PDF  $f$ e que desejamos gerar observações e $Y$  uma outra variável aleatória com PDF $h$ no mesmo suporte de $f$. A variável aleatória $Y$ é escolhida de tal forma que sabemos gerar suas observações. Então o algoritmo do método da aceitação e rejeição é definido pelos passos que seguem:

\begin{enumerate}
	\item Gere uma observação de $y$ proveniente de $Y$;
	\item Gere uma observação $u$ de uma variável aleatória $U\sim \mathcal{U}(0, 1)$;
	\item Se $u < \frac{f(y)}{cg(y)}$,  em que $c$ é uma constante real, aceite $x = y$; caso contrário rejeite $y$ como observação de $X$ e volte ao passo 1.
\end{enumerate}
A constante $c$ deve ser escolhida de tal forma que $\frac{f(y)}{cg(y)} \leq 1$. Considerando o caso discreto, em que também é possível aplicar o método da aceitação e rejeição, se $\{aceita\} = \{x = y\} = \{u < \frac{f(y)}{cg(y)}\}$, então,

$$P(\{aceitar\}| Y = y) = \frac{P(\{aceitar\} \cap {Y=y})}{g(y)} = \frac{P\left( U \leq  \frac{f(y)}{cg(y)}\right)g(y)}{g(y)} = \frac{f(y)}{cg(y)}.$$

Daí, pelo Teorema da Probabilidade Total, temos que:

$$P(\{aceitar\}) = \sum_y P(\{aceitar\}| Y  = y) = \frac{1}{c}.$$

Sendo assim, para minimizar o custo computacional de se gerar obervações de $X$ por meio de observações geradas de $Y$, colhe-se $c$ como o menor valor possível para maximizar a probabilidade de aceitação acima. Maiores detalhes do método da aceitação e rejeição poderá ser encontrado em Rizzo (2019).
}

\begin{table}[H]
	\centering
	\caption{Mean biases of the MLEs obtained using the BFGS method calculated from the Monte-Carlo simulation.}\label{tab:bias}
	\begin{tabular}{rrrrrrr}
		\hline
		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
		\hline
		10 & 0.2376 & 2.1635 & 2.7557 & 1.6282 & 1.3057 & 1.1430\\
		20 & 0.4154 & 2.4639 & 1.5728 & 1.8082 & 0.7383 & 1.6248\\
		60 & 0.7214 & 2.2432 & 0.5667 & 1.8815 & 0.2872 & 3.3954\\
		100 & 0.6146 & 1.9579 & 0.3253 & 1.6148 & 0.2651 & 4.9628\\
		200 & 0.3838 & 1.3894 & 0.1827 & 1.1773 & 0.3701 & 8.1457\\
		400 & 0.2166 & 0.9635 & 0.1076 & 0.6181 & 0.3957 & 13.7370\\
		600 & 0.1269 & 0.7242 & 0.0772 & 0.3968 & 0.3637 & 17.9310\\
		1,000 & 0.0553 & 0.4885 & 0.0521 & 0.2328 & 0.2636 & 22.8784 \\
		2,000  &  0.0456 & 0.3087 &  0.0334 &  0.0990 & 0.1722 &  38.4593\\
		5,000 & -0.0058 & 0.1307 & 0.0146 & 0.0117 & 0.0171 & 52.8098\\
		10,000 & -0.0146 & 0.0842 & 0.0095 & 0.0095 & 0.0031 & 95.8380\\
		20,000 & -0.0090 & 0.0330 & 0.0038 & 0.0005 & -0.0099 & 126.4260\\
		30,000 & -0.0028 & 0.0183 & 0.0012 & -0.0036 & -0.0029 & 182.0760\\
		50,000 & -0.0057 & 0.0124 & 0.0015 & 0.0016 & -0.0021 & 291.9300\\
		\hline
	\end{tabular}
\end{table}

@@

\item 
Rizzo, Maria L. Statistical computing with R. CRC Press (2019).
